Secure Composition \\ of Robust and Optimising Compilers

### 2024-09-24 csf2/main.tex
drop novelty claim

This section introduces trace properties of interest for this paper: \gls*{tms}, \gls*{sms}, \gls*{ms}, \gls*{scct}, and \gls*{ss}.
These properties are of practical importance (as mentioned in \Cref{sec:introduction}) and also of interest in the case study presented later (\Cref{sec:casestud:defs,sec:casestud:rtp}). 
This section presents all of them, despite the fact that only property \gls*{scct} is novel and the others are inspired by existing work, in order to showcase all that is required for a formal proof of security for a realistic compilation toolchain.
%\MP{ say something about this in the rebuttal: only the defs are borrowed, the universal images and all that work is new}
%\MK{ universal images are not new. }
% , none of the properties is novel, for self-containment of the paper, their definition is necessary for the case study.
For each of the presented properties, the technical report defines corresponding monitors, which refine a given property and have a key role in the proofs of this paper. 
% managed to prove 
%  if tms-monitor --[trace]-->* ∅  
%  then trace ∈ tms
% but not
%  if trace ∈ tms
%  then tms-monitor --[trace]-->* ∅

>>>>

This section introduces trace properties of interest for this paper: \gls*{tms}, \gls*{sms}, \gls*{ms}, \gls*{scct}, and \gls*{ss}.
These properties are of practical importance (as mentioned in \Cref{sec:introduction}) and also of interest in the case study presented later (\Cref{sec:casestud:defs,sec:casestud:rtp}). 
This section presents all of them, despite the fact that they are inspired by existing work, in order to showcase all that is required for a formal proof of security for a realistic compilation toolchain.
%\MP{ say something about this in the rebuttal: only the defs are borrowed, the universal images and all that work is new}
%\MK{ universal images are not new. }
% , none of the properties is novel, for self-containment of the paper, their definition is necessary for the case study.
For each of the presented properties, the technical report defines corresponding monitors, which refine a given property and have a key role in the proofs of this paper. 
% managed to prove 
%  if tms-monitor --[trace]-->* ∅  
%  then trace ∈ tms
% but not
%  if trace ∈ tms
%  then tms-monitor --[trace]-->* ∅
